%-----------EXPERIENCE-----------
\section{Work Experience}
    \resumeSubHeadingListStart
    
    \resumeSubheading
        {Software Developer (part-time) - Alyf GmbH}{November. 2021 - Present}
        {\href{https://github.com/alyf-de}{github.com/alyf-de}}{Dublin, Ireland}
        \resumeItemListStart
            \resumeItem {ERPNext ({\href{https://github.com/frappe/erpnext}{github.com/frappe/erpnext}})}
                \resumeItemListStart
                    \resumeItem{Refactored the subscriptions module to fix incorrect invoices created, making it on par with other Subscription SaaS offerings. Reduce the code complexity and improve coverage for the subscriptions module by 18\%.}
                \resumeItemListEnd
            \resumeItem {Frappe Framework ({\href{https://github.com/frappe/frappe}{github.com/frappe/frappe}})}
                \resumeItemListStart
                    \resumeItem{Rebuilt the parts of the localization feature of the frappe framework for modules like the setup wizard, forms dashboards and the primary-secondary relationship field controller as certain elements were being incorrectly translated.}
                \resumeItemListEnd
            \resumeItem {Datatable ({\href{https://github.com/frappe/datatable}{github.com/frappe/datatable}})}
                \resumeItemListStart
                    \resumeItem{Implemented translation module in the datatable library to enable seamless integration in the Frappe Framework.}
                \resumeItemListEnd
        \resumeItemListEnd
    \vspace{+8pt}
    \resumeSubheading
        {Senior Engineer - Bloomstack Technologies Pvt Ltd.}{September. 2020 - August. 2021}
        {\href{https://github.com/Bloomstack}{github.com/Bloomstack}}{Mumbai, India}
        \resumeItemListStart
            \resumeItem{Mentored and supported a team of five developers, supervising all aspects of sprint planning, feature development, and bug fixes, increasing overall productivity by 15\% and improving the code quality and stability of the codebase by 11\%.}
            \resumeItem {Bloomtrace}
                \resumeItemListStart
                    \resumeItem{Slashed the infrastructure expenses by 9\%, enhanced the system performance and throughput by 17\%, and eliminated downtime by redesigning Bloomtrace's architecture (PaaS to abstract and automate the complexity of the US government's cannabis compliance).}
                \resumeItemListEnd
            \resumeItem {Frappe Framework ({\href{https://github.com/Bloomstack/frappe}{github.com/Bloomstack/frappe}})}
                \resumeItemListStart
                    \resumeItem{Minimized the legal risks for customers that could arise due to incorrect datetime associated with time-sensitive documents like Contracts, Service Level Agreements, Sales, and Purchase Invoices, by overhauling the Timezone API and making datetime objects timezone aware.}
                    \resumeItem{Eliminated the rounding-off issue faced by the customers during yearly auditing by refactoring the Precision API to save values in the database with high precision of 9 places.}
                \resumeItemListEnd
        \resumeItemListEnd
    \vspace{+8pt}
    \resumeSubheading
        {Software Developer - Frappe Technologies Pvt Ltd.}{September. 2018 - August. 2020}
        {\href{https://github.com/Frappe}{github.com/frappe}}{Mumbai, India}
        \resumeItemListStart
            \resumeItem{//Seibert /Media GmbH}
                \resumeItemListStart
                    \resumeItem{Managed and led the development for building //Seibert /Media core features and bug fixes for Frappe Framework and ERPNext for 1+ years.}
                    \resumeItem{Engineered a custom solution for eliminating Frappe ORM bottlenecks and system downtimes for continued data insertion from external systems, cutting the infrastructure expenses by 20\%. Set up an up-time monitoring system with their existing infrastructure to monitor Frappe and ERPNext deployment in case of any downtime.}
                \resumeItemListEnd
            \resumeItem{In-App Support Infrastructure for ERPNext Cloud and Self-Hosted}
                \resumeItemListStart
                    \resumeItem{Restructured the support pipeline at Frappe Technologies and engineered an In-App Support Module, reducing L1 support servicing overhead by 23\% and improved support bug fixes by 15\%, ensuring higher availability and faster resolution for all issues raised by clients.}
                \resumeItemListEnd
            \resumeItem{ERPNext ({\href{https://github.com/frappe/erpnext}{github.com/frappe/erpnext}})}
                \resumeItemListStart
                    \resumeItem{Conceptualized and implemented Service Level Agreements in ERPNext's Support module, improving the module efficiency and user experience by 41\% and built dashboards for better customer support analytics.}
                \resumeItemListEnd
            \resumeItem{Frappe Framework ({\href{https://github.com/frappe/frappe}{github.com/frappe/frappe}})}
                \resumeItemListStart
                    \resumeItem{Strengthened IP security restrictions to enforce strict IP and session validation whenever the user tried to establish a session with the server.}
                    \resumeItem{Refactored the Communications module to improve execution time by 6\% and allow for the easy linking of receiving emails to documents based on the unique document id embedded in the email id, allowing users to send emails from email providers and letting the framework link them to the relevant document.}
                \resumeItemListEnd
        \resumeItemListEnd
  \resumeSubHeadingListEnd